---
title: "Statistical Inference - Project Part 1"
author: "Rafael Mejia"
date: "19 de noviembre de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this document you can show the answers and inllustrations of the inferential data analysis. This document consists of the first part "A simulation excercise".

## Initial data

```{r}

#set seed for reproducibility
set.seed(31)

#set lambda to 0.2
lambda <- 0.2

#40 samples
n <- 40

#1000 simulations
simulations <- 1000

#simulate
simulated_exponentials <- replicate(simulations, rexp(n, lambda))

#calculate the mean of exponentials
means_exponentials <- apply(simulated_exponentials, 2, mean)


```


## Question 1

Show where the distribution is centered at and compare it to the theorical center of the distribution.

```{r}
#distribution mean

analytical_mean <- mean(means_exponentials)
analytical_mean

#analytical mean
theory_mean <-1/lambda
theory_mean

#visualization
hist(means_exponentials, xlab = "mean", main = "Exponential function Simulations")
abline(v = analytical_mean, col = "green")
abline(v = theory_mean, col = "orange")


```

### Answer 1
The analytical mean is 4.993867 the theoretical mean is 5.
The center of distribution of averages of 40 exponentials is very close to the theoretical center of the distribution.

## Question 2

Show how variable it is and compare it to the theoretical variance of the distribution.

```{r}
# standard deviation of distribution
standard_deviation_dist <- sd(means_exponentials)
standard_deviation_dist

# standard deviation from analytical expression
standard_deviation_theory <-(1/lambda)/sqrt(n)
standard_deviation_theory

# variance of distribution
variance_dist <- standard_deviation_dist^2
variance_dist

# variance from analytical expression
variance_theory <- ((1/lambda)*(1/sqrt(n)))^2
variance_theory

```

# Answer 2
Stadard Deviation of the distribution is 0.7937608 with the theoretical SD calculatedas 0.7905694.
The Theoretical variance is calculated as ((1/lambda)*(1/sqrt(n)))^2 = 0.625
The actual variance of the distribution is 0.6291041

## Question 3

Show that the distribution is approximately normal.

```{r}
xfit <- seq(min(means_exponentials), max(means_exponentials),length=100)
yfit <- dnorm(xfit,mean=1/lambda, sd=(1/lambda/sqrt(n)))
hist(means_exponentials, breaks = n, prob=T, col="light blue", xlab = "means", main = "Density of means", ylab = "density")
lines(xfit, yfit, pch = 22, col = "red", lty = 5)

```

